First Journal proof on Article LZ15969

### 2019-06-19 eg6-letters/incoherent/journal-proof/proof_cover1/journal_proof1.tex
added the response to the 1st proof

\title{First Journal proof on Article LZ15969)}

@@

\begin{enumerate}
   \item  PRL prefers to refer to the current article as ``Letter.'' Please 
      indicate when terms such as ``study'' and/or ``work'' can be changed to 
      ``Letter'' throughout the article or when the terms ``study'' and 
      ``work'' refer to the larger body of research behind the Letter.

   \item Journal style dictates that acronyms not appear in the abstract unless 
   they occur more than once.

\item Copyediting changes have been made to your article to conform to APS 
   style and improve readability. Please check to make sure changes have not 
      altered your intended meaning.

\item Please supply a definition for ``EMC'' as it is not on our list of 
   acronyms not needing definition. Journal style dictates that acronyms be 
      defined at their first occurrence in the body of the article.

   \item Please check the sentence beginning ``The previous measurements of 
      DVCS...'' to be sure your meaning has not been changed.

\item Please note the change to outer square brackets throughout the article to 
   avoid nested fences of the same size and type per PRL style.

      \item Please check all equations carefully to be sure errors were not 
         introduced during conversion.

      \item Please supply a definition for ``PDF'' as it is not on our list of 
         acronyms not needing to be defined and there is more than one possible 
         definition. Journal style dictates that acronyms used only once in the 
         body of the article be spelled out and the acronym deleted.

\item Journal style dictates that full words, abbreviations, and acronyms with 
   more than one letter appearing in the inferior or superior positions be set 
      roman.

\item PRL prefers italic font for single-letter acronyms and single-letter 
   variables and abbreviations in text and in math.

\item Please review the funding information section of the proof's cover letter 
   and respond as appropriate. We must receive confirmation that the funding 
      agencies have been properly identified before the article can publish.

\item This query was generated by an automatic reference checking system.  
   Reference [18] could not be located in the databases used by the system.  
      While the references may be correct, we ask that you check them so we can 
      provide as many links to the referenced articles as possible.

\item NOTE: External links, which appear as blue text in the reference section, 
   are created for any reference where a Digital Object Identifier (DOI) can be 
      found. Please confirm that the links created in this PDF proof, which can 
      be checked by clicking on the blue text, direct the reader to the correct 
      references online. If there is an error, correct the information in the 
      reference or supply the correct DOI for the reference. If no correction 
      can be made or the correct DOI cannot be supplied, the link will be 
      removed.

   \item  APS now requires that journal references with authors numbering 10 or 
      fewer display all author names. Please verify author names in expanded 
      author list for Ref. [8].

\item Please provide publication information for Ref. [41] if available.

>>>>

\title{First Journal proof on Article LZ15969}

@@

\begin{enumerate}
   \item  PRL prefers to refer to the current article as ``Letter.'' Please 
      indicate when terms such as ``study'' and/or ``work'' can be changed to 
      ``Letter'' throughout the article or when the terms ``study'' and 
      ``work'' refer to the larger body of research behind the Letter.\\
      \textcolor{blue}{Response: the word ``work'' can be changed to ``Letter'' 
      in Line 73. We prefere to keep the word ``work'' as it is in F5:2. }

   \item Journal style dictates that acronyms not appear in the abstract unless 
      they occur more than once.\\
      \textcolor{blue}{Response: We are fine with this edit, i.e., removing 
      ``DVCS'' acronym. }

\item Copyediting changes have been made to your article to conform to APS 
   style and improve readability. Please check to make sure changes have not 
      altered your intended meaning.\\
      \textcolor{blue}{Response: Everything looks good. }

\item Please supply a definition for ``EMC'' as it is not on our list of 
   acronyms not needing definition. Journal style dictates that acronyms be 
      defined at their first occurrence in the body of the article.\\
      \textcolor{blue}{Response: ``EMC'' stands for ``European Muon 
      Collaboration'' }

   \item Please check the sentence beginning ``The previous measurements of 
      DVCS...'' to be sure your meaning has not been changed.\\
      \textcolor{blue}{Response: your edit of adding ``they are'' to this 
      sentence is fine for us. Nothing has been changed in terms of the 
      meaning. }

\item Please note the change to outer square brackets throughout the article to 
   avoid nested fences of the same size and type per PRL style.\\
      \textcolor{blue}{Response: Everything looks good on this aspect. }

      \item Please check all equations carefully to be sure errors were not 
         introduced during conversion.\\
      \textcolor{blue}{Response: The equations are fine.}

      \item Please supply a definition for ``PDF'' as it is not on our list of 
         acronyms not needing to be defined and there is more than one possible 
         definition. Journal style dictates that acronyms used only once in the 
         body of the article be spelled out and the acronym deleted.\\
      \textcolor{blue}{Response: ``PDFs'' stands for ``parton distribution 
      functions'' }

\item Journal style dictates that full words, abbreviations, and acronyms with 
   more than one letter appearing in the inferior or superior positions be set 
      roman.\\
      \textcolor{blue}{Response: We are fine with this modification of 
      $t_{min}$.}

\item PRL prefers italic font for single-letter acronyms and single-letter 
   variables and abbreviations in text and in math.\\
      \textcolor{blue}{Response: We are find with this change of ``k'' }

\item Please review the funding information section of the proof's cover letter 
   and respond as appropriate. We must receive confirmation that the funding 
      agencies have been properly identified before the article can publish.\\
      \textcolor{blue}{Response: The funding agencies are properly identified.  
      }

\item This query was generated by an automatic reference checking system.  
   Reference [18] could not be located in the databases used by the system.  
      While the references may be correct, we ask that you check them so we can 
      provide as many links to the referenced articles as possible.\\  
      \textcolor{blue}{Response: These are some links to the paper:\\
     DOI:10.1140/epjc/s2005-02345-3\\        arXiv:hep-ex/0505061}

\item NOTE: External links, which appear as blue text in the reference section, 
   are created for any reference where a Digital Object Identifier (DOI) can be 
      found. Please confirm that the links created in this PDF proof, which can 
      be checked by clicking on the blue text, direct the reader to the correct 
      references online. If there is an error, correct the information in the 
      reference or supply the correct DOI for the reference. If no correction 
      can be made or the correct DOI cannot be supplied, the link will be 
      removed.\\
      \textcolor{blue}{Response: All the links are working fine. }

   \item  APS now requires that journal references with authors numbering 10 or 
      fewer display all author names. Please verify author names in expanded 
      author list for Ref. [8].\\
      \textcolor{blue}{Response: The full author list is correct.}

\item Please provide publication information for Ref. [41] if available.\\
      \textcolor{blue}{Response: We can provide this direct link to this 
      reference \url{https://tel.archives-ouvertes.fr/tel-01218756/document}}
